### 2019-02-11 2-Chapters/4-Chapter/chapter4.tex
Almost done for copy/pastying the chapter 4 based on 4 publications (the longer)
I should start to include the code of articles, and not just the skeleton

@@

\input{2-Chapters/4-Chapter/CROWNCOM2017.tex}

@@

\input{2-Chapters/4-Chapter/ICT2018_and_WCNC2019.tex}

@@

\input{2-Chapters/4-Chapter/WCNC2019_restransmissions.tex}

@@

@@

>>>>

\TODOL{Write a nice introduction for this chapter.}

\TODOL{Present outline of the chapter.}

\TODOL{Give list of publications associated with this chapter.}

@@

% - ``Multi-Armed Bandit Learning in IoT Networks and non-stationary settings'', see https://hal.inria.fr/hal-01575419

\input{2-Chapters/4-Chapter/CrownCom_17.git/IoT_slotted.tex}

@@

% - ``MALIN: Multi-Arm bandit Learning for Iot Networks with GRC: A TestBed Implementation and Demonstration that Learning Helps'', demo at ICT, and the companion paper ``GNU Radio Implementation of MALIN: "Multi-Armed bandits Learning for Internet-of-things Network"'', see https://hal.inria.fr/hal-02006825

\input{2-Chapters/4-Chapter/IEEE_WCNC_2019__DemoICT.git/main.tex}

@@

\input{2-Chapters/4-Chapter/IEEE_WCNC__2019__Paper__BMBM.git/IEEE_WCNC__2019__Paper__BMBM.tex}

@@

\TODOL{Write a conclusion, and future works}

@@

% \TODOL{Include here additional results (proof in Section from CROWNCOM ?)}
\input{2-Chapters/4-Chapter/CrownCom_17.git/IoT_slotted_appendix.tex}
